LaMachine: A meta-distribution for NLP software

### 2018-09-10 docs/lamachine_extabstract_clarin2018.tex
[paper] reworded beginning of software section

As LaMachine was conceived initially as the primary means of distribution of the software stack developed at CLST, Radboud University
Nijmegen, it includes a lot of our software. LaMachine exists since May 2015 and has been used extensively ever since
by numerous users. A full list of included software goes beyond the scope of this overview; we will merely mention
some CLARIN-NL/CLARIAH-funded tools: ucto (a tokeniser), Frog (an NLP suite for Dutch), FoLiA (Format for Linguistic
Annotation, with assorted tools), FLAT (a web-based linguistic Annotation tool), PICCL (an OCR and post-OCR correction
pipeline) and CLAM. We already include some relevant software by the University of Groningen (such as Alpino, a
dependency parser) and VU Amsterdam as well. Moreover, LaMachine incorporates a large number of renowned tools by
external international parties, offering most notably a mature Python environment with renowned scientific modules such
as scipy, numpy, scikit-learn, matplotlib, nltk, spacy, pytorch, keras, gensim, and many others, but also R, Java and tools
such as Stanford CoreNLP.

>>>>

LaMachine exists since May 2015 and has been used extensively ever since by numerous users. It was initiallly conceived
as the primary means of distribution of the software stack developed at CLST, Radboud University Nijmegen, it includes a
lot of our software.  A full list of included software goes beyond the scope of this overview; we will merely mention
some CLARIN-NL/CLARIAH-funded tools: ucto (a tokeniser), Frog (an NLP suite for Dutch), FoLiA (Format for Linguistic
Annotation, with assorted tools), FLAT (a web-based linguistic Annotation tool), PICCL (an OCR and post-OCR correction
pipeline) and CLAM. We already include some relevant software by the University of Groningen (such as Alpino, a
dependency parser) and VU Amsterdam as well. Moreover, LaMachine incorporates a large number of renowned tools by
external international parties, offering most notably a mature Python environment with renowned scientific modules such
as scipy, numpy, scikit-learn, matplotlib, nltk, spacy, pytorch, keras, gensim, and many others, but also R, Java and
tools such as Stanford CoreNLP.
